---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Init directories and load required libraries

```{r, echo=TRUE}
setwd('/home/babl/coursera/Reproducible_Research/pa1')
library(data.table)
library(ggplot2)
library(grid)
library(gridExtra)
```

## Loading and preprocessing the data

```{r,echo=TRUE}
data<-data.table(read.csv("activity.csv", header=TRUE, na.strings="NA"))
```

## What is mean total number of steps taken per day?

### Make a histogram of the total number of steps taken each day

```{r,echo=TRUE}
total_steps_by_date <- aggregate(steps ~ date, data, 'sum', na.rm=TRUE)
mean_steps_by_date <- aggregate(steps ~ date, data, 'mean', na.rm=TRUE)

plot1 <- ggplot(mean_steps_by_date, aes(x=steps)) +
  geom_histogram(binwidth=5, colour="black", fill="white") +
  ggtitle('Mean of the total steps / day')

plot2 <- ggplot(total_steps_by_date, aes(x=steps)) +
  geom_histogram(binwidth=1000, colour="black", fill="white") +
  ggtitle('Total number of steps / day')

grid.arrange(plot1,plot2,ncol=2)
```

### Calculate and report the mean and median total number of steps taken per day

```{r, echo=TRUE}
mean<-mean(total_steps_by_date$steps,na.rm=TRUE)
median<-median(total_steps_by_date$steps,na.rm=TRUE)
```
```{r, echo=TRUE}
print(mean)
```
```{r, echo=TRUE}
print(median)
```

The mean of total number of steps taken per day are `r mean` and median are `r median`.

## What is the average daily activity pattern?

```{r, echo=TRUE}
mean_steps_by_interval <- aggregate(steps ~ interval, data, 'mean', na.rm=TRUE)
ggplot(mean_steps_by_interval, aes(x = interval, y = steps)) + geom_line()
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
